---
title: "Type coercion"
author: "Rachel Good"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

-   `c(1, 1L, "C")`
```{r}
c(1, 1L, "C")
```
Concatenated variables turned to character
```{r}
1
1L
"C"
```
double, integer, character
```{r}
typeof(c(1, 1L, "C"))
```
concatenated character
-   `c(1L / 0, "A")`

```{r}
c(1L / 0, "A")
```
concatenated character
```{r}
typeof(1L)
typeof(0)
typeof(1L/0)
typeof("A")
```
integer, double, error, character
```{r}
typeof(c(1L / 0, "A"))
```
concatenated character
-   `c(1:3, 5)`

```{r}
c(1:3, 5)
```
concatenated doubles
```{r}
typeof(1:3)
typeof(5)
```
double, integer
```{r}
typeof(c(1:3, 5))
```
concatenated double
-   `c(3, "3+")`

```{r}
c(3, "3+")
```
concatenated character
```{r}
typeof(3)
typeof("3+")
```
integer, character
```{r}
typeof(c(3, "3+"))
```
-   `c(NA, TRUE)`

```{r}
c(NA, TRUE)
```
concatenated logical
```{r}
typeof(NA)
typeof(TRUE)
```
logical, logical
```{r}
typeof(c(NA, TRUE))
```
concatenated logical
## References {#references}
1. Assignment Adapted from [Mine Cetinkaya-Rundel's Data Science in a Box](https://github.com/rstudio-education/datascience-box)